Dynastic Extinctions and Urban Economic Development: \\Evidence from the Holy Roman Empire\footnote{I thank Davide Cantoni, Matthias Weigand, and my RA colleagues at the Chair of Economic History for helpful comments and feedback.}

### 2023-05-13 paper/paper.tex
#15 structure rquestion-economics-metrics
#15 add thoughts on research question

\section{Introduction}

@@

\section{Literature review}

@@

\section{Cities, lineages, and territories}

% #####################################################

\section{Empirical approach}

% #####################################################

\section{Results}

% #####################################################

\section{Validity and robustness}

>>>>

Make me care.
Make the reader care. That's your challenge.

@@

\section{Research Question}

When a ruling dynasty goes extinct, what happens to their lands?

\subsection{Disambiguation}
Let me be more precise. Concepts to be defined:
\begin{itemize}
    \item[ruling dynasty] In the context of the HRE. Until the 19th century geopolitics was not done in terms of nation-states, but in terms of the territorial holdings of noble families.
    \item[their lands] The cities in that dynasty's possession at the time of its extinction.
    \item[what happens] It's complicated and precisely this is what I need to clarify first.
\end{itemize}

What \textit{could} it mean?
\begin{itemize}
    \item economic prosperity.
    \item public goods provision.
    \item quality of government.
\end{itemize}

The whole thing is that construction by itself is just barely not interesting enough. i need just one intermediate step to motivate me using construction.

i could be intellectually honest and just state the process i went through. i initially thought about economic prosperity, then it didn't line up with the wages, then i focused on public goods and ruler commitment instead.

and i can actually do all of those by splitting my construction variable up! one outcome variable with all buildings (as a benchmark), another with public goods buildings, and the other with representative buildings.

I love that idea.

So my chain of reasoning will go the following way:
\begin{itemize}
    \item get to stating the research question in the shortest possible way
    \item explain ruling dynasty
    \item explain their lands
    \item explain the aspects i'm interested in: economic prosperity, public goods provision, ruler commitment / quality of government
\end{itemize}

Where in this do i discuss the issue with the wages? The intro is no place for it, but i can't bring economic prosperity up as a serious goal of the analysis in the intro if i'm going to discredit it two sections later. i need to be cautious about it from the start, maybe mention it as a detour / side note but refer to the wages figure in the appendix.

John H. Cochrane says "Figure out the \textit{one} central and novel contribution of your paper. Write this down in one paragraph. As with all your writing, this must be concrete."

My central contribution is the finding that dynastic extinctions have (no/an/X) effect on urban economic development.

\subsection{Issues to address}

What are the most interesting aspects of that, for the purpose of this thesis? Which are the issues I want to discuss? What are secondary research questions?

The effect of size changes is a secondary research question.

@@

\section{The Economics / Hypotheses}

\section{The Econometrics / Evidence}
